---
title: "10 simple rules for teaching R for Data Science"  
author: 
  - "Tiffany Timbers (UBC)"
  - "`r Sys.Date()`"
date: 'bit.ly/timbers-cascadia-r-conf-2022'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: '%current%'
      titleSlideClass: [top, left]
      ratio: '16:9'

---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message = FALSE, 
                      echo = FALSE, 
                      warning = FALSE,
                      fig.align = "center")
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#9F999C",
  secondary_color = "#FFE5F3",
  inverse_header_color = "#8F8C8E",
  link_color = "deeppink",
  title_slide_text_color = "#3d3d3d",
  title_slide_background_image = "img/title-slide-background-light.png",
  title_slide_background_position = "left",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```


class: middle


---

class: middle

## Summary

1. Teach R by doing data analysis - and teach the skills you need to do it as you go. Helps with motivation.
2. Live code!
3. Give students tons and tons of practice!
4. Give students tons and tons of feedback!
5. Use tractable toy data examples
6. Use real data sets
7. Provide cultural and historical context
8. Build a safe, inclusive and welcoming community
9. Utilize/facilitate peer learning
10. Use realistic projects to link concepts/tasks together

---

class: middle

## Acknowledgements


- UBC Master of Data Science students

- UBC DSCI 100 and 310 students

- UBC Master of Data Science teaching team

- The Carpentries

---

## References

1. 

---


class: inverse, center, middle

## 10 simple rules for teaching R for Data Science?

#### talk slides: *[https://bit.ly/timbers-cascadia-r-conf-2022](https://bit.ly/timbers-cascadia-r-conf-2022)*
